---
title: "assignment 4"
author: "pavan"
date: "23/10/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
# setting working directory and loading packages

```{r }
setwd("C:/Users/pavankumar pendela/Desktop/MSBA/Quantiative management Dr.Wu/assignment 4")
library(lpSolve)
library(lpSolveAPI)
```

```{r }
lpec <- make.lp(5,6)
set.objfn(lpec, c(622,614,630,641,645,649))
lp.control(lpec, sense = "min")
```
```{r }
# Production Capacity Constraints:
set.row(lpec, 1, c(1,1,1), indices = c(1,2,3))
set.row(lpec, 2, c(1,1,1), indices = c(4,5,6))
# Warehouse demand Constraints:
set.row(lpec, 3, c(1,1), indices = c(1,4))
set.row(lpec, 4, c(1,1), indices = c(2,5))
set.row(lpec, 5, c(1,1), indices = c(3,6))
# Setting the rhs values
rhs <- c(100,120,80,60,70)
set.rhs(lpec, rhs)
# Setting the constraint type
set.constr.type(lpec, c("<=","<=","=","=","="))
```

```{r}
# boundary condiiton for the decision variables
set.bounds(lpec, lower = rep(0, 6))
# Set the names of the rows (constraints) and columns (decision variables)
lp.rownames <- c("Plant A capacity", "Plant B capacity", "warehouse 1 demand", "warehouse 2 demand", "Warehouse 3 Demand")
lp.colnames <- c("PlantA to warehouse1", "PlantA to warehouse2", "PlantA to warehouse3", "PlantB to warehouse1", "PlantB to warehouse2", "Plant B to warehouse3")
dimnames(lpec) <- list(lp.rownames, lp.colnames)
```

```{r}
# Return the linear programming object to ensure the values are correct
lpec
write.lp(lpec, filename = "assignment 4 lp", type = "lp")
```
# Solve the linear program
```{r}
solve(lpec)
```
"0" is the optimal solution for the problem

```{r}
get.objective(lpec)
```
1,32,790 is the production cost based on the given values

```{r}
get.variables(lpec)
```
Plant A Units Shipped to warehouse 1: 0 units 
Plant A Units Shipped to warehouse 2: 60 units 
Plant A Units Shipped to warehouse 3: 40 units 
Plant B Units Shipped to warehouse 1: 80 units 
Plant B Units Shipped to warehouse 2: 0 units 



