---
title: "assignment-5"
author: "pavan"
date: "07/11/2021"
output:
  word_document: default
  html_document: default
---
```{r}
setwd("C:/Users/pavankumar pendela/Desktop/MSBA/Quantiative management Dr.Wu/assignment 5")
```
# installing packages
```{r}
library(Benchmarking)
library(tidyverse)
```

COMPUTE THE FORMULATION

```{r}
# creating the vectors with our values
input  <-  matrix(c(150,400,320,520,350,  320,  200,  700,  1200,  2000,  1200,  700),ncol  =  2) 
output <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000, 15000),ncol = 2)
# Assigning column names
colnames(output) <- c("staff_daily_hours","supplies_daily")
colnames(input) <- c("daily_reimbursed_patient", "daily_privately_paid_patient")
# values of input & output
input
output
```
As you can see, we're obtaining the same results as the performance data table from Hope Valley Health Care Association's six nursing facilities.

Now, we use "DEA" tool that can help organizations to identify and allocate their resources to enhance their efficiency and have better practices.

# DEA analysis using FDH
```{r}

analysis_fdh<-  dea(input,output,RTS  =  "fdh")

eff_fdh <- as.data.frame(analysis_fdh$eff)

colnames(eff_fdh)  <-  c("efficiency_fdh")

peer_fdh  <-  peers(analysis_fdh)

colnames(peer_fdh) <- c("peer1_fdh")

lambda_fdh <- lambda(analysis_fdh)

colnames(lambda_fdh) <- c("L1_fdh", "L2_fdh", "L3_fdh", "L4_fdh", "L5_fdh", "L6_fdh")

peer_lamb_eff_fdh  <-  cbind(peer_fdh,  lambda_fdh,  eff_fdh)

peer_lamb_eff_fdh
```


```{R}
# Plot the results
dea.plot(input,output,RTS="fdh", main="Free disposability hull (FDH) Graph")

```

# DEA analysis using CRS
```{r}

analysis_crs <- dea(input,output,RTS = "crs")

eff_crs <- as.data.frame(analysis_crs$eff)

colnames(eff_crs) <- c("efficiency_crs")

peer_crs <- peers(analysis_crs)

colnames(peer_crs) <- c("peer1_crs", "peer2_crs", "peer3_crs")

lambda_crs <- lambda(analysis_crs)

colnames(lambda_crs) <- c("L1_crs", "L2_crs", "L3_crs", "L4_crs")

peer_lamb_eff_crs <- cbind(peer_crs, lambda_crs, eff_crs)

peer_lamb_eff_crs

```

```{r}
# Plot the results
dea.plot(input,output,RTS="crs", main="Constant Returns to Scale (CRS) Graph")

```

# DEA Analysis using VRS
```{r}

analysis_vrs  <-  dea(input,output,RTS  =  "vrs")

eff_vrs <- as.data.frame(analysis_vrs$eff)

colnames(eff_vrs)  <-  c("efficiency_vrs")

peer_vrs <- peers(analysis_vrs)

colnames(peer_vrs) <- c("peer1_vrs", "peer2_vrs", "peer3_vrs")

lambda_vrs <- lambda(analysis_vrs)

colnames(lambda_vrs) <- c("L1_vrs", "L2_vrs", "L3_vrs", "L4_vrs", "L5_vrs")

peer_lamb_eff_vrs <- cbind(peer_vrs, lambda_vrs, eff_vrs)

peer_lamb_eff_vrs


```

```{r}
# Plot the results
dea.plot(input,output,RTS="vrs", main="Variable Returns to Scale (VRS) Graph")

```
# DEA Analysis using IRS
```{r}

analysis_irs  <-  dea(input,output,RTS  =  "irs")

eff_irs <- as.data.frame(analysis_irs$eff)

colnames(eff_irs)  <-  c("efficiency_irs")

peer_irs <- peers(analysis_irs)

colnames(peer_irs)  <-  c("peer1_irs",  "peer2_irs",  "peer3_irs")

lambda_irs  <-  lambda(analysis_irs)

colnames(lambda_irs) <- c("L1_irs", "L2_irs", "L3_irs", "L4_irs", "L5_irs")

peer_lamb_eff_irs <- cbind(peer_irs, lambda_irs, eff_irs)

peer_lamb_eff_irs
```

```{r}
# Plot the results
dea.plot(input,output,RTS="irs",  main="Increasing  Returns  to  Scale  (IRS) Graph")

```
# DEA Analysis using DRS
```{r}

analysis_drs  <-  dea(input,output,RTS  =  "drs")

eff_drs <- as.data.frame(analysis_drs$eff)

colnames(eff_drs)  <-  c("efficiency_drs")

peer_drs <- peers(analysis_drs)

colnames(peer_drs) <- c("peer1_drs", "peer2_drs", "peer3_drs")

lambda_drs <- lambda(analysis_drs)

colnames(lambda_drs) <- c("L1_drs", "L2_drs", "L3_drs", "L4_drs")

peer_lamb_eff_drs <- cbind(peer_drs, lambda_drs, eff_drs)

peer_lamb_eff_drs

```
```{r}
# Plot the results
dea.plot(input,output,RTS="drs", main="Decreasing Returns to Scale (DRS) Graph")

```
# DEA Analysis using FRH

```{r}

analysis_frh  <-  dea(input,output,RTS  =  "add")

eff_frh <- as.data.frame(analysis_frh$eff)

colnames(eff_frh) <- c("efficiency_frh")

peer_frh <- peers(analysis_frh)

colnames(peer_frh) <- c("peer1_frh")

lambda_frh <- lambda(analysis_frh)

colnames(lambda_frh) <- c("L1_frh", "L2_frh", "L3_frh", "L4_frh", "L5_frh", "L6_frh")

peer_lamb_eff_frh <- cbind(peer_frh, lambda_frh, eff_frh)

peer_lamb_eff_frh

```
```{r}
# Plot the results
dea.plot(input,output,RTS="add", main="Free Replicability Hull (FRH) Graph")

```
# Compare between different assumptions

```{r}
dea.plot(input,output,RTS="fdh", main="Free disposability hull (FDH) Graph")

dea.plot(input,output,RTS="vrs", main="Variable Returns to Scale (VRS) Graph")

dea.plot(input,output,RTS="drs", main="Decreasing Returns to Scale (DRS) Graph")

dea.plot(input,output,RTS="irs",  main="Increasing  Returns  to  Scale  (IRS)  Graph")

dea.plot(input,output,RTS="crs", main="Constant Returns to Scale (CRS) Graph")

dea.plot(input,output,RTS="add", main="Free Replicability Hull (FRH) Graph")

```
These charts allow us to compare the results of each DEA model.
"All DEA models share the premise of estimating the technology using a minimum extrapolation technique," according to what we studied in this session (DEA Slides).

FDH is the smallest technology set, as can be shown. It seeks to create fewer outputs (number of patient days reimbursed by third-party sources and number of patient days reimbursed privately) with more inputs (number of patient days reimbursed by third-party sources and number of patient days reimbursed privately) (staffing labor and the cost of supplies). FDH is the most popular model among businesses, yet it has several flaws owing to its assumptions. As we can see, all of the efficiencies in this model are 1, however it is not as efficient as we thought when compared to other models since we identify areas/units to improve.

VRS is larger than FDH because it “fills-out” the spaces that FDH reduced. Here we can see that unit 6 can improve its efficiency.

As the graphs show, DRS and IRS are bigger than VRS. For smaller input values, DRS seeks to enlarge the set, whereas the IRS tries to raise the technology. Units 5 and 6 might increase their efficiency, according to DRS, and facility 6 could improve as well, according to IRS.

CRS is the largest technology set, allowing us to assess whether there are any conceivable scaling up or down combinations. Units 5 and 6 require improvement based on the efficiency numbers.

The purpose of FRH, which is larger than FDH but less than CRS, is to replace deterministic data with random variables.


## Q 2 - Research and Development Division of Emax Corporation

Objective function:

max: 20 X1 + 15 X2 + 25 X3 - 6 Y1P - 6 Y1M - 3 Y2M
S.T :
Employment Level

6x1 + 4x2 + 5x3 - (Y1P - Y1M)  = 50

Earnings Next Year
 
8x1 + 7x2 + 5x3 - (Y2P - Y2M)  = 75
 
Nonnegativity  contraint
 

X1, X2, X3 >= 0
Y1P, Y1M, Y2P, Y2M >= 0

```{r}
library(lpSolveAPI)
setwd("C:/Users/pavankumar pendela/Desktop/MSBA/Quantiative management Dr.Wu/assignment 5")
# Load the data
emax <-  read.lp("emax.lp")
emax
```

```{r}
solve(emax)
```
As we can see, the solver is returning 0, indicating that it is finding a solution.

```{r}
get.objective(emax)
```
We are maximizing profit while reducing other company goals such as manpower and profits in this scenario. The penalty for failing to meet the goals on the objective function is 225.

```{r}
get.variables(emax)
```
This order is from how the variables were written in the objective function. In our case, the results are as follows: X1 = 0,X2 = 0,X3 = 15,Y1P = 25,Y1M = 0,Y2M = 0,Y2P = 0 which means that the earnings (y2) expectations are fully satisfied.
Regarding the workforce, the goal projected is exceded by 25 and based on the total profit of product 3, it has a negative result on its profit by 15.